Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-03-27 src/tex/ms.tex

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
    \caption{Caption}
    \label{fig:ofe-distribution-yields}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models (a--d) and as observed by APOGEE (e). Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right. Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex. Model (a) assumes the fiducial parameters and the \yZ{1} yield set, whereas models (b--d) assume the \yZ{2} yield set. Model (c) also adopts a power-law SN Ia DTD, while in model (d) the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$. {\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent when assuming higher yields and outflows. This effect can be mitigated by pre-enriched infall.}
    \label{fig:ofe-df}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}. The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model which assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$. {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
    \label{fig:abundance-evolution-params}
\end{figure*}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_yields.pdf}
    \caption{Stellar [O/Fe] distributions produced by multi-zone models which assume different yield sets and outflow mass-loading factors. Each row presents stellar distributions within a range of absolute midplane distance $|z|$ reported on the far right. Within each panel, the distributions are color-coded according to the bin in galactocentric radius $R_{\rm gal}$ from which they are drawn. Each distribution is normalized so that the area under the curve is 1, and the vertical scale is consistent across each row. The median APOGEE abundance uncertainties are forward-modeled onto the model outputs (see Table \ref{tab:uncertainties}). For visual clarity, each distribution is smoothed with a box-car of width 0.05 dex. {\bf Key takeaway:} The two-infall model produces an intermediate-[O/Fe] peak that is especially prominent in the \yZ{2} model at mid to high latitudes.}
    \label{fig:ofe-distribution-yields}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{src/tex/figures/ofe_distribution_params.pdf}
    \caption{Stellar [O/Fe] distributions produced by select multi-zone models with \yZ{2} (a--d) and as observed by APOGEE (e). The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} the fiducial model with \yZ{2}, the fiducial DTD, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$ (identical to column (b) of Figure \ref{fig:abundance-evolution-yields}); {\bf (b)} a model that adopts a power-law DTD; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.7$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.24$. {\bf Key takeaway:} For the \yZ{2} case, pre-enrichment of the accreted gas or a higher thick-to-thin disk ratio}
    \label{fig:ofe-df}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/abundance_evolution_params.pdf}
    \caption{Stellar age--abundance relations produced by select multi-zone models with \yZ{1}. The layout is similar to Figure \ref{fig:abundance-evolution-yields}. Each column shows results from a different multi-zone model: {\bf (a)} our fiducial model with $y/Z_\odot=1$, $\sigma_{\rm RM8}=2.7\,{\rm kpc}$, pristine gas infall, and $f_\Sigma(R_\odot)=0.12$; {\bf (b)} a model with greater radial migration strength $\sigma_{\rm RM8}=5\,{\rm kpc}$; {\bf (c)} a model that assumes the infalling gas has metallicity $\mathOH_{\rm CGM}=\mathFeH_{\rm CGM}=-0.5$; and {\bf (d)} a model with a higher local thick-to-thin disk ratio, $f_\Sigma(R_\odot)=0.48$. {\bf Key takeaway:} Model (d) comes the closest to the observed age--metallicity relation at the expense of the age--[O/Fe] relation, but no model completely reconciles the dilution problem.}
    \label{fig:abundance-evolution-params}
\end{figure*}
